XXXXX

### 2014-09-22 paper/paper1.tex
appendix

\subsection{allowed usage of constructs in class expressions}

\subsection{supported constructs in OWL 2 QL}

\subsection{not supported constructs in OWL 2 QL}

\section{RDF Validation Requirements Expressible By OWL 2 QL}

\section{RDF Validation Requirements Not Expressible By OWL 2 QL}

@@

@@

\begin{table}
\caption{RDF Validation Requirements Covered by OWL 2 QL}
\label{tab:RequirementsCoveredOWL2QL}
\centering
\begin{tabular}{lcccccccc}
\hr
Requirements \\
\hr
R-1-UNIQUENESS-OF-URIS \\
R-2-UNIQUE-INSTANCES \\
R-3-EQUIVALENT-CLASSES \\
R-4-EQUIVALENT-OBJECT-PROPERTIES \\
R-5-EQUIVALENT-DATA-PROPERTIES \\
\hr
\end{tabular}
\end{table}

@@

\begin{table}
\caption{RDF Validation Requirements Not Covered by OWL 2 QL}
\label{tab:RequirementsNotCoveredOWL2QL}
\centering
\begin{tabular}{lcccccccc}
\hr
Requirements \\
\hr
R-6-EQUIVALENT-INDIVIDUALS \\
\hr
\end{tabular}
\end{table}

>>>>

\section{RDF Validation Requirements Not Covered By OWL 2 QL}

@@

\subsection{Allowed Usage of Constructs in Class Expressions in OWL 2 QL}

\subsection{Supported Constructs in OWL 2 QL}

\subsection{Not Supported Constructs in OWL 2 QL}

@@

\begin{table}
\caption{RDF Validation Requirements Covered by OWL 2 QL}
\label{tab:RequirementsCoveredOWL2QL}
\centering
\begin{tabular}{ll}
\hr
Requirements Classification & Requirements \\
\hr
& R-1-UNIQUENESS-OF-URIS \\
& R-2-UNIQUE-INSTANCES \\
& R-3-EQUIVALENT-CLASSES \\
& R-4-EQUIVALENT-OBJECT-PROPERTIES \\
& R-5-EQUIVALENT-DATA-PROPERTIES \\
& R-7-DISJOINT-CLASSES \\
& R-9-DISJOINT-OBJECT-PROPERTIES \\
& R-10-DISJOINT-DATA-PROPERTIES \\
& R-14-DISJOINT-INDIVIDUALS \\
\hr
\end{tabular}
\end{table}

@@

\begin{table}
\caption{RDF Validation Requirements Not Covered by OWL 2 QL}
\label{tab:RequirementsNotCoveredOWL2QL}
\centering
\begin{tabular}{lc}
\hr
Requirements & Covering Constraint Languages \\
\hr
R-6-EQUIVALENT-INDIVIDUALS & OWL 2 DL \\
R-8-DISJOINT-UNION-OF-CLASS-EXPRESSIONS & OWL 2 DL \\
R-11-DISJOINT-DATA-PROPERTIES-CLASS-SPECIFIC & ShEx \\
R-12-DISJOINT-OBJECT-PROPERTIES-CLASS-SPECIFIC & ShEx \\
R-13-DISJOINT-GROUP-OF-PROPERTIES-CLASS-SPECIFIC & ShEx \\
\hr
\end{tabular}
\end{table}
